%-------------------------
% Resume in Latex
% Author : Nisarg Gajjar
% Tailored for SDE Role
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generated PDF is ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small#4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Nisarg Gajjar} \\ \vspace{1pt}
    \small +91-7016801458 $|$ \href{mailto:nisargg705@gmail.com}{\underline{nisargg705@gmail.com}} $|$
    \href{https://www.linkedin.com/in/nisargg705/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Nisrgg}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT Bhopal University}{Sehore, MP}
      {Bachelor of Technology in Computer Science and Engineering; CGPA: 9.04/10.0}
      {Aug 2022 – Aug 2026}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Programming Languages}: C++, Go (Golang), Kotlin, Python}
  \resumeItem{\textbf{Frameworks \& Tools}: Jetpack Compose, Retrofit, Hilt, Gin, Scrapy, Docker, Chi, sqlc}
  \resumeItem{\textbf{Databases}: PostgreSQL, SQL, Firebase Firestore}
  \resumeItem{\textbf{Other}: REST APIs, Firebase Authentication, MVVM Architecture, Material Design 3, Data Cleaning (Pandas, NumPy)}
\resumeItemListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeItemListStart
  \resumeItem{GitHub Foundation}
  \resumeItem{Oracle Certified - Data Platform 2025 Foundations Associate}
  \resumeItem{Meta Certified - Android Developer Professional}
\resumeItemListEnd



%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Jio Platforms Limited}{Sept 2024 – Nov 2024}
    {Office Seat Occupancy Detection System $|$ \href{https://github.com/Nisrgg/Office-Seat-Occupancy-Detection}{\underline{GitHub}}}{}
    \resumeItemListStart
      \resumeItem{Developed a comprehensive data science system using Python, OpenCV, and YOLOv5 for real-time office seat occupancy detection and analysis with high accuracy.}
      \resumeItem{Implemented modular architecture with configuration management, statistical analysis engine, and automated reporting capabilities, significantly reducing manual monitoring effort.}
      \resumeItem{Built interactive data visualization dashboards and Jupyter notebooks for occupancy pattern analysis, generating actionable insights for space optimization.}
      \resumeItem{Designed comprehensive test suite with pytest, implemented CLI interface, and created professional documentation following software engineering best practices.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Swaasthya - Hospital Management System} $|$ \emph{Kotlin, Go, PostgreSQL, Firebase Auth, Jetpack Compose} $|$ \href{https://github.com/Nisrgg/Swaasthya}{\underline{GitHub}}}{}
    \resumeItemListStart
      \resumeItem{Developed a full-stack healthcare management system with Android app (Kotlin/Jetpack Compose) and Go backend API, serving patients, doctors, and hospital staff with secure authentication and role-based access.}
      \resumeItem{Implemented RESTful API using Go/Gin framework with PostgreSQL database, Firebase JWT authentication, Docker containerization, and comprehensive CRUD operations for appointments and doctor management.}
      \resumeItem{Built modern Android UI with Material Design 3, MVVM architecture using Hilt dependency injection, Retrofit for API integration, and secure configuration management with environment variables.}
      \resumeItem{Designed responsive doctor listing with search/filter capabilities, appointment booking system, and comprehensive security measures including network security configuration and proper secret management.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RSSync - RSS Feed Aggregator} $|$ \emph{Go (Golang), PostgreSQL, Docker, Chi, sqlc} $|$ \href{https://github.com/Nisrgg/RSSync}{\underline{GitHub}}}{}
    \resumeItemListStart
      \resumeItem{Developed a scalable RESTful API in Go using the Chi router for managing users, feeds, and subscriptions, leveraging sqlc for type-safe database interactions.}
      \resumeItem{Engineered a concurrent background worker to periodically scrape RSS/Atom feeds, parse XML content, and store posts in a PostgreSQL database.}
      \resumeItem{Containerized the database using Docker for reproducible environments and implemented secure, stateful API key-based authentication middleware.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACADEMIC & COMPETITIVE CODING-----------
\section{Academic \& Competitive Coding}
\resumeItemListStart
  \resumeItem{Achieved \textbf{Top 1\%} rank in NPTEL Cloud Computing (24,000+ students).}
  \resumeItem{Solved 150+ coding problems on LeetCode, strengthening proficiency in DSA and algorithms.}
\resumeItemListEnd




%-----------EXPERIENCE-----------
\section{Co-Curricular Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Treasurer}{Aug 2024 – Jan 2025}
  {Bashcraft Club}{Campus}
  \resumeItemListStart
    \resumeItem{Spearheaded strategic planning and execution of high-impact technical events, including ideathons with 300+participants to promote innovation and collaboration.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
